%-------------------------
% Resume in Latex
% Author : Asish Kumar (migrated from oldresume)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref} % hidelinks removes boxes/colors
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{iftex}
\ifPDFTeX
  \input{glyphtounicode}
\fi


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\ifPDFTeX
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Asish Kumar} \\ \vspace{1pt}
    \small +919204664622 $|$ \href{mailto:officialasishkumar@gmail.com}{officialasishkumar@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/asish-kr/}{Linkedin} $|$
    \href{https://github.com/officialasishkumar}{Github}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bharati Vidyapeeth's College of Engineering, New Delhi}{New Delhi, India} % College Name & Location
      {B. Tech. - Information Technology; GPA - 8.2/10}{December 2021 -- June 2025} % Degree, GPA & Dates
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
{Keploy}{Bangalore, Karnataka, India}
{Software Engineer}{August 2025 - Present}
\resumeItemListStart
    \resumeItem{Developed a test de-duplication feature using UNIX sockets, removing redundant cases to enhance test accuracy.}
    \resumeItem{Deployed a high-performance secret sanitization feature to secure over 1,000 test cases in under 30 seconds.}
    \resumeItem{Built a MongoDB mocking engine that decodes the native wire protocol to accurately record database calls and uses a concurrent, fingerprint-based algorithm to instantly match live requests to the correct mock.}
    \resumeItem{Built a Playwright-based Kubernetes regression pipeline for Keploy's cloud record-replay flow, provisioning Kind clusters in CI and hardening UI/API replay checks to catch end-to-end failures reliably.}
    \resumeItem{Resolved 50+ customer-reported issues in Keploy for Allen, an enterprise customer, delivering product bug fixes and feature enhancements across the record-replay platform.}
\resumeItemListEnd

    \resumeSubheading
      {Google Summer of Code}{Remote} % Company & Location
      {Open Source Contributor @CHAOSS}{May 2025 -- August 2025}
        \resumeItemListStart
              \resumeItem{Delivered an end-to-end contributor analytics feature, creating a new data model and collection worker in Augur to process community engagement.}
            \resumeItem{Designed funnel and radar charts in 8Knot to visualize contributor retention and activity for project maintainers.}
        \resumeItemListEnd

      \resumeSubheading
      {Narration Box}{Remote}
      {Software Engineering Intern}{January 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Drove a 60\% increase in weekly active users by launching and optimizing new feature sets.}
        \resumeItem{Designed and implemented RESTful APIs using Django REST Framework and integrated Hasura for a real-time GraphQL layer, supporting the core AI narration service.} 
      \resumeItemListEnd
    
    \resumeSubheading
      {Google Summer of Code}{Remote} % Program/Org & Location
      {Open Source Contributor @TARDIS-SN}{May 2024 -- September 2024} % Role & Dates
      \resumeItemListStart
        \resumeItem{Implemented 30 benchmarks covering 80\% of the codebase, boosting test reliability and performance coverage.}
        \resumeItem{Optimized GitHub Actions with caching, setup, and custom parameters, cutting runtime by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Linux Foundation Mentorship Program}{Remote} % Program/Org & Location
      {Open Source Contributor @KCL Language}{June 2024 -- August 2024} % Role & Dates
      \resumeItemListStart
        \resumeItem{Implemented Sparse-checkout, enabling KPM to add a repo sub-directory as a 3rd-party dependency.}
        \resumeItem{Added new unit tests that cover 600+ lines of code and improved the overall coverage to 40.616\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SQL Cache} $|$ \emph{Go, MySQL, Docker, REST APIs} $|$ \href{https://github.com/officialasishkumar/sql-cache}{GitHub}}{March 2026} % Project Name, Tech, Link & Date
          \resumeItemListStart
            \resumeItem{Built a production-style Go backend backed by MySQL and Docker Compose, exposing REST endpoints for customers, products, and orders.}
            \resumeItem{Integrated a SQL record-and-replay layer that captures live query responses into YAML mocks and replays them in offline mode without a running database.}
            \resumeItem{Improved MySQL compatibility in the caching layer by normalizing byte-encoded values during capture and replay, making mocks human-readable and reliable for local development.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TrieQuest} $|$ \emph{React, TypeScript, FastAPI, SQLAlchemy, MySQL, Docker, Three.js, Playwright} $|$ \href{https://github.com/officialasishkumar/TrieQuest}{GitHub}}{March 2026} % Project Name, Tech, Link & Date
          \resumeItemListStart
            \resumeItem{Built a full-stack competitive programming platform where users form squads, share problems from 8 coding platforms, track analytics, and create challenges -- deployed on Vercel and Render with a Dockerized MySQL backend.}
            \resumeItem{Designed a Trie-based autocomplete engine for O(k) prefix search on usernames and problem titles, replacing SQL ILIKE with an in-memory index populated at startup and kept in sync on writes.}
            \resumeItem{Implemented an in-memory Bloom filter with SHA-256 double-hashing for O(1) username availability checks, eliminating redundant database queries during registration.}
            \resumeItem{Developed a multi-dimensional analytics engine with time-window filtering, platform-specific difficulty mapping, activity trends, and leaderboards visualized via Recharts.}
            \resumeItem{Secured the API with JWT + Argon2 hashing, fixed-window rate limiting, CORS hardening, and engineered 12 interactive algorithm visualizations from scratch with React and Framer Motion.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item\small{
        \begin{itemize}[leftmargin=0in, itemsep=1pt, topsep=2pt]
            \item {Rated \href{https://codeforces.com/profile/AsishKumar}{Specialist} on CodeForces with max rating: 1469, solving over 1350+ problems.}
            \item {Knight with 1850+ rating (top 5.5\%) on \href{https://leetcode.com/u/openSUSE/}{Leetcode}, solving over 600+ problems.}
            \item {Qualified For ACM ICPC onsite regionals, 2022 held at Mathura, Uttar Pradesh.}
        \end{itemize}
    }
 \end{itemize}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages (4)}{: Python, Go, JavaScript, SQL, HTML, CSS} \\
     \textbf{Frameworks/Libraries (12)}{: React.js, Next.js, Node.js, Express.js, GraphQL, Zustand, SocketIO, airspeed velocity, cProfile, memray} \\ 
     \textbf{Developer Tools (7)}{: Git, Docker, MongoDB, Linux shell, RudderStack, GitHub Actions, MySQL} \\ 
     \textbf{Concepts (3)}{: Data Structures \& Algorithms, DBMS Fundamentals, Computer Networks Fundamentals}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

